---
title: "Sorting Journals"
subtitle: "Overview about Journals and their scores"
author: "Thorsten Höser, thorsten.hoser@gmail.com, [Researchgate](https://www.researchgate.net/profile/Thorsten_Hoeser), [GitHub](https://github.com/thho)"

date: "`r paste(Sys.Date())`"
output:
  html_document:
    fig_caption: true
    fig_crop: true
    toc: true
    toc_float: 
      smooth_scroll: true
      collapsed: false
    toc_depth: 3
    number_sections: false
urlcolor: blue
fontsize: 11pt
---
```{r searchkey, include=FALSE}
skey <- c('14764687', '0169555X')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(knitr)
library(kableExtra)
```

# About SCImago Journal Rank

"*SCImago Journal Rank (SJR indicator) is a measure of scientific influence of scholarly journals that accounts for both the number of citations received by a journal and the importance or prestige of the journals where such citations come from. A journal's SJR is a numeric value indicating the average number of weighted citations received during a selected year per document published in that journal during the previous three years. Higher SJR values are meant to indicate greater journal prestige.*" (https://en.wikipedia.org/wiki/SCImago_Journal_Rank)

The data used in this overview is from https://www.scimagojr.com/journalrank.php

```{r echo=FALSE, warning=FALSE}
#get data from SJR
#download.file("https://www.scimagojr.com/journalrank.php?out=xls", destfile = "./srjdata.csv")
dat <- read.csv("./scimagojr 2018.csv", sep = ";", stringsAsFactors = F)#, quote = '')
mergestring<-  read.csv("./scimagojr 2018.csv", header = FALSE, sep = "$", stringsAsFactors = F)
mergestring <- mergestring$V1[2:nrow(mergestring)]
```

# Journals in Remote Sensing

```{r echo=FALSE}
#which('Remote Sensing' == dat$Categories)
index <- grepl('Remote Sensing', mergestring)
rs.jour <- dat[index, ]
rs.jour$Title <- paste("[",rs.jour$Title, "](https://www.scimagojr.com/journalsearch.php?q=", rs.jour$Issn, ")", sep = "")

rs.jour <- data.frame(rs.jour$Title,
                      rs.jour$Issn,
                      rs.jour$Type,
                      rs.jour$SJR,
                      rs.jour$H.index,
                      rs.jour$Publisher)
colnames(rs.jour) <- substr(colnames(rs.jour), 9, 100)
rs.jour <- as.matrix(rs.jour)
```

```{r results="asis", echo=FALSE}
kable(rs.jour, 
      caption="", 
      align = rep("c", ncol(rs.jour))) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# My Selection

```{r echo=FALSE}
#which('Remote Sensing' == dat$Categories)
index <- sapply(skey, function (y) sapply(mergestring, function (x) grepl(y, x)))
index <- apply(index, MARGIN = 1, FUN = function (x) Reduce("|", x))#choose "&" for AND operator for key words

rs.jour <- dat[index, ]
rs.jour$Title <- paste("[",rs.jour$Title, "](https://www.scimagojr.com/journalsearch.php?q=", rs.jour$Issn, ")", sep = "")

rs.jour <- data.frame(rs.jour$Title,
                      rs.jour$Issn,
                      rs.jour$Type,
                      rs.jour$SJR,
                      rs.jour$H.index,
                      rs.jour$Publisher)
colnames(rs.jour) <- substr(colnames(rs.jour), 9, 100)
rs.jour <- as.matrix(rs.jour)
```

```{r results="asis", echo=FALSE}
kable(rs.jour, 
      caption="", 
      align = rep("c", ncol(rs.jour))) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Journals from MDPI

```{r echo=FALSE}
#which('Remote Sensing' == dat$Categories)
index <- grepl('MDPI', mergestring)
rs.jour <- dat[index, ]
rs.jour$Title <- paste("[",rs.jour$Title, "](https://www.scimagojr.com/journalsearch.php?q=", rs.jour$Issn, ")", sep = "")

rs.jour <- data.frame(rs.jour$Title,
                      rs.jour$Issn,
                      rs.jour$Type,
                      rs.jour$SJR,
                      rs.jour$H.index,
                      rs.jour$Publisher)
colnames(rs.jour) <- substr(colnames(rs.jour), 9, 100)
rs.jour <- as.matrix(rs.jour)
```

```{r results="asis", echo=FALSE}
kable(rs.jour, 
      caption="", 
      align = rep("c", ncol(rs.jour))) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

